### 2025-01-27 our_article/MCM_article/article_file.tex
论文的重要更新

  \section{Sensitivity Analysis}
  \section{Evaluation of the Model}
    \subsection{Strengths}
    \subsection{Weaknesses}
  \section{Suggestions}

>>>>

  \section{Sensitivity Analysis}
    We consider the effects of changes in two types of model parameters on the system: 
    the initial values of biomass density \( W \) in the dynamic model and typical environmental parameters. 
    The sensitivity analysis of the system is conducted over a time range of 0 to 80 weeks. 
    During this period, the agricultural ecosystem model corresponds to a chemical-use system that considers species re-migration (Model III). 
    Given that rice is the primary producer and crop in this agricultural ecosystem, 
    the figures in the following discussion use the time evolution of rice biomass as a representative example.

    \subsection{Changes in Initial Biomass Density}
      The initial values of all biomass densities \( W \) in the system are set to three different values: 
      the original values as shown in Chapter 4 figures, five times the original values, and 20\% of the original values. 
      These scenarios simulate the diversity of converted forest conditions and agricultural environments. 
      The resulting curves are shown in Figure \ref{fig:Change_init}.

      \begin{figure}[H]
        \centering
        \includegraphics[width=0.75\linewidth]{images/Change_init.png}
        \caption{Impact of Initial Biomass Density Changes on System Dynamics}
        \label{fig:Change_init}
      \end{figure}

      From the figure, we observe that the biomass curves representing the three initial conditions converge after a relatively long period of natural evolution. 
      Similar patterns are observed for other populations in the ecosystem. 
      This demonstrates that our agricultural ecosystem model possesses a degree of self-regulation, 
      consistent with the stability and self-recovery capabilities of real-world ecological systems.

    \subsection{Changes in Typical Environmental Parameters}
      Let's examine the effects of changes in four typical environmental parameters that significantly influence the system: 
      the natural growth rate of rice biomass \( r_{crp} \), 
      the weed-to-rice competition coefficient \( \beta_{c\rightarrow w} \), 
      the environmental maximum biomass carrying capacity for rice \( \mathscr{K}_{crp} \), 
      and the standard deviation of Gaussian white noise \( \sigma \). 
      Each parameter is set to three different values (as indicated in the figures below), 
      and the resulting curves are plotted in Figure \ref{fig:Change_all}. 
      In the plots related to \( \beta_{c\rightarrow w} \), 
      we also include the time evolution of weed biomass for comparison with rice.

    \begin{figure}[H]
      \includegraphics[width=\linewidth]{images/Change_all.png}
      \caption{Impact of Changes in Key Environmental Parameters on System Dynamics}
      \label{fig:Change_all}
    \end{figure}

    Below, we analyze the curves for each of the four scenarios:
    \begin{itemize}
      \item Effect of \( r_{crp} \) (natural growth rate of rice biomass):** 
      As shown in Figure \ref{fig:Change_all} (A), an increase in \( r_{crp} \) leads to an upward trend in rice biomass at any given time, and vice versa. 
      From an ecological perspective, an increase in \( r_{crp} \) indicates a higher marginal growth rate of rice biomass, resulting in faster growth, 
      which aligns with the figure. On the other hand, 
      the overall evolutionary trend of the system remains approximately the same when \( r_{crp} \) varies within a certain range, 
      reflecting the system's stability.
      \item Effect of \( \beta_{c\rightarrow w} \) (weed-to-rice competition coefficient):** As shown in Figure \ref{fig:Change_all} (B), 
      an increase in \( \beta_{c\rightarrow w} \) results in a downward trend in rice biomass and an upward trend in weed biomass at any given time, 
      and vice versa. Ecologically, an increase in \( \beta_{c\rightarrow w} \) reflects a higher competitive ability of weeds relative to rice, 
      enabling weeds to gain an advantage in interspecies competition, which is consistent with the figure. 
      Moreover, the overall evolutionary trend of the system remains approximately the same when \( \beta_{c\rightarrow w} \) varies within a certain range, 
      demonstrating system stability.
      \item Effect of \( \mathscr{K}_{crp} \) (maximum carrying capacity for rice):** As shown in Figure \ref{fig:Change_all} (C), 
      an increase in \( \mathscr{K}_{crp} \) results in an upward trend in rice biomass at any given time, and vice versa. 
      Ecologically, an increase in \( \mathscr{K}_{crp} \) indicates a higher potential maximum biomass for rice, 
      with rice biomass gradually approaching this value under suitable growth conditions, consistent with the figure. 
      Similarly, the overall evolutionary trend remains stable within a certain range of \( \mathscr{K}_{crp} \), further reflecting system stability.
      \item Effect of \( \sigma \) (standard deviation of Gaussian white noise):** As shown in Figure \ref{fig:Change_all} (D), 
      when \( \sigma \) is within a certain range, the trend of rice biomass over time remains approximately the same, 
      further demonstrating that the system's overall evolutionary trend is essentially unaffected. 
      Since \( \sigma \) is positively correlated with the amplitude of random fluctuations in the system, 
      this reflects the system's stability. However, it is noted that when \( \sigma = 0.1 \), rice goes extinct around week 70. 
      This occurs because large random fluctuations cause severe negative disturbances in the dynamics of rice biomass, 
      leading to its rapid decline to zero when the growth rate of \( W_{crp} \) is relatively low. 
      This illustrates that the system's stability and resilience to disturbances are finite, 
      which is consistent with the ecological concept of limited resistance and recovery in ecosystems.
    \end{itemize}
  \section{Evaluation of the Model}
    \subsection{Strengths}
    \subsection{Weaknesses}
  \section{Suggestions}
